---
title: "Stock-recruitment analysis for Atnarko sockeye"
author: "D. Greenberg"
date: "10/25/2022"
output:
  html_document:
  toc: true
  toc_depth: 2
  toc_float:
    collapsed: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```

```{r load,  include=FALSE}
library(here);library(ggplot2);library(rstan);library(cowplot)
```
```{r, functions}
source(here('code','stan_functions.R'))
source(here('code','lfo_stan_functions.R'))
source(here('code','util_functions.R'))
source(here('code','RP_functions.R'))
```

The goal of this document is to examine stock-recruitment dynamics in Atnarko sockeye, using the historical time-series of recruitment for brood cohorts from 1972 to 2016.

We start by visualizing recruits as a function of spawner escapement, by brood year.

```{r, data, warning = FALSE, results = FALSE}
SR_data <- read.csv(here('data','Atnarko_SK_RS.csv'));SR_data2<- read.table(here('data','Atnarko_SK_RS_v_CM.txt'),header=T)
names(SR_data)[1]=c('broodyear')
SR_data$logR_S<- log(SR_data$recruits/SR_data$spawners)
SR_data<- SR_data[complete.cases(SR_data$logR_S),]
SR_data2$logR_S<- log(SR_data2$RS);SR_data2<- SR_data2[complete.cases(SR_data2$logR_S),]
#pdf of figure:
#pdf(here('figures','Figure 1.pdf'),width=8,height=6)
#ggplot(SR_data, aes(spawners, recruits)) +
#  geom_point(aes(colour = broodyear),size=2.5) +
#  scale_colour_viridis_c()
#dev.off()

ggplot(SR_data, aes(spawners, recruits)) +
  geom_point(aes(colour = broodyear),size=2.5) +
  scale_colour_viridis_c(name='Year')+xlab("Spawners") + ylab("Recruits")+theme(axis.text=element_text(size=11),
        axis.title=element_text(size=12,face="bold"))

```

Figure 1. Recruitment as a function of spawner escapement for Atnarko sockeye from brood year cohorts 1972 to 2016.

\pagebreak
## Model Selection
We will use the Atnarko sockeye stock-recruitment time-series to compare 8 different stock-recruitment model forms that represent time-invariant (models 1 & 2), time-varying (models 3 - 5), or regime-shift (models 6 - 8) model types. For the sake of brevity we will omit the finer details of these models - but by comparing these different forms we can ask whether the data best support either static stock-recruitment dynamics or non-stationary stock-recruitment dynamics in the form of either continuous changes in the parameters or through distinct shifts between stock regime states.

Model 1 - Static Ricker curve

Model 2 - Autocorrelated Ricker curve

Model 3 - Time-varying productivity Ricker curve

Model 4 - Time-varying capacity Ricker curve

Model 5 - Time-varying prod. & cap. Ricker curve

Model 6 - Regime-shift productivity Ricker curve

Model 7 - Regime-shift capacity Ricker curve

Model 8 - Regime-shift prod. & cap. Ricker curve

We start by competing each of these models in their accuracy in predicting productivity (log Recruits per Spawner) 1-year ahead using an iterative cross-validation approach (implemented with functions from samEst, https://github.com/Pacific-salmon-assess/samEst), starting from the 16th brood cohort and onwards. Note, for this analysis we have adjusted the default priors on stock capacity from samEst to be more informative for Atnarko sockeye based on a capacity prior estimate from Atlas et al. 2021 (https://www.biorxiv.org/content/10.1101/2021.03.22.436497v1). We set the expected capacity to be ~18000, with 1 standard deviation (on the natural log scale) ranging from 6600 to 43000.


```{r, echo=FALSE,results='hide'}
#Because model selection takes so long, it's easier to just run that section and load the loglikelihood results (logliks.RData) from 'data'. To run through this yourself, see the 'model_selection_atnarko.R' file in code that will produce this output.

load(here('data','logliks.RData'))
```

Using the out-of-sample log-likelihood estimates, we can compare the Bayesian model weights for each model set. First finding the highest likelhood prediction window (ie 1-year back parameters, last 3-year average of parameters, or last 5-year average of parameters). We can assess model weights using the full predictive dataset, or dropping the 10/20% of hardest to assess years as the full model likelihoods may be highly influenced by the most challenging to predict observations.

```{r, model selection}
  wm2=which.max(apply(ll2,1,sum)) #select best likelihood from different timeframes (1-y back, 3-y back, 5-y back)
  wm3=which.max(apply(ll3,1,sum))#best fit for model 3
  wm4=which.max(apply(ll4,1,sum))#best fit for model 4
  wm5=which.max(apply(ll5,1,sum)) #best fit for model 5
  wm6=which.max(apply(ll6,1,sum)) #best fit for model 6
  wm7=which.max(apply(ll7,1,sum)) #best fit for model 7
  wm8=which.max(apply(rbind(ll8_1,ll8_2),1,sum)) #best fit for model 8 (two combinations of higher alpha, lower cap; higher alpha, higher cap)
  if(wm8<4){
    mod_loglik=rbind(ll1,ll2[wm2,],ll3[wm3,],ll4[wm4,],ll5[wm5,],ll6[wm6,],ll7[wm7,],ll8_1[wm8,])
    rownames(mod_loglik)[1:8]=paste('m',seq(1:8),sep='');rownames(mod_loglik)[8]='m8_1'
  }
  if(wm8>4){
    mod_loglik=rbind(ll1,ll2[wm2,],ll3[wm3,],ll4[wm4,],ll5[wm5,],ll6[wm6,],ll7[wm7,],ll8_2[wm8-4,])
    rownames(mod_loglik)[1:8]=paste('m',seq(1:8),sep='');rownames(mod_loglik)[8]='m8_2'
  }

  model_weights(mod_loglik)
  model_weights(mod_loglik,type='d90')
  model_weights(mod_loglik,type='d80')
```

Using the 1-year out-of-sample predictive accuracy from 1987 to 2016, the best supported model was the static model with autocorrelated residuals (model 4), with regime-shift capacity (model 4) and regime-shift productivity having the next highest level of support based on the 90% and 80% highest accuracy observations, respectively. 

We'll proceed by fitting and visualizing these three models to the full dataset.



```{r, mod preds, warning = FALSE}
x_new=seq(min(SR_data$spawners),max(SR_data$spawners),length.out=200)

#predicted fits for each model
#m2 - ac ricker
alpha.m2=median(d2$log_a)
beta.m2=median(d2$b)

y_pred_d2=exp(alpha.m2-beta.m2*x_new)*x_new

resids=apply(d2$epsilon,2,median)
resid.l90=apply(d2$epsilon,2,quantile,0.1)
resid.u90=apply(d2$epsilon,2,quantile,0.9)
resid.df=data.frame(resids,resid.l90,resid.u90,by=SR_data2$year)

#m6 - regime alpha
alpha.m6=apply(d6$log_a,2,median)
beta.m6=median(d6$b)

y_pred_d6.1=exp(alpha.m6[1]-beta.m6*x_new)*x_new
y_pred_d6.2=exp(alpha.m6[2]-beta.m6*x_new)*x_new

#m7 - regime beta
alpha.m7=median(d7$log_a)
beta.m7=apply(d7$b,2,median)

y_pred_d7.1=exp(alpha.m7-beta.m7[1]*x_new)*x_new
y_pred_d7.2=exp(alpha.m7-beta.m7[2]*x_new)*x_new

pred_df=data.frame(x_new,y_pred_d2,y_pred2,y_pred_d6.1,y_pred_d6.2,y_pred_d7.1,y_pred_d6.2)


#Probability for each regime
SR_data$p.High_Cap=apply(d7$gamma[,,1],2,median)
SR_data$p.High_Prod=apply(d6$gamma[,,2],2,median)

gamma_d_m6=data.frame(prob=apply(d6$gamma[,,2],2,median),l90=apply(d6$gamma[,,2],2,quantile,0.1),u90=apply(d6$gamma[,,2],2,quantile,0.9),by=SR_data$broodyear)
gamma_d_m7=data.frame(prob=apply(d7$gamma[,,1],2,median),l90=apply(d7$gamma[,,1],2,quantile,0.1),u90=apply(d7$gamma[,,1],2,quantile,0.9),by=SR_data$broodyear)
#pdf(here('figures','Figure 2.pdf'),width=8,height=6)
#ggplot(SR_data, aes(spawners, recruits)) +
#  geom_point(aes(colour = broodyear),size=2.5) +
#  scale_colour_viridis_c()+geom_line(data=pred_df,aes(x=x_new,y=y_pred1))+geom_line(data=pred_df,aes(x=x_new,y=y_pred2))
#dev.off()

SR_data2=cbind(SR_data2,resid.df[,1:3])
```

```{r, figure 2m2, warning = FALSE}
ggplot(SR_data, aes(spawners, recruits)) +
  geom_point(aes(colour = broodyear),size=2.5,) +
  scale_colour_viridis_c(name = "Year")+geom_line(data=pred_df,aes(x=x_new,y=y_pred_d2))+xlab("Spawners") + ylab("Recruits")+theme(axis.text=element_text(size=11),
        axis.title=element_text(size=12,face="bold"))
```

Figure 2. a) Predicted stock-recruitment functions for Atnarko sockeye, with observations coloured by brood cohort year, from the top-rated model (Ricker curve with autocorrelated residuals) for the full predictive window from 1987 to 2016. b) Residual productivity from brood years 1972 to 2016. 

Autocorrelation of the residuals is moderate to high:
```{r, ac}
fg2c=hist(d2$rho,xlab='Autocorrelation coefficient',main='',bins=30,xlim=c(0,1))
summary(d2$rho)
```

```{r, figure 2m7, warning = FALSE}
ggplot(SR_data, aes(spawners, recruits)) +
  geom_point(aes(colour = broodyear),size=2.5) +
  scale_colour_viridis_c(name = "Year")+geom_line(data=pred_df,aes(x=x_new,y=y_pred_d7.1))+geom_line(data=pred_df,aes(x=x_new,y=y_pred_d7.2))+xlab("Spawners") + ylab("Recruits")+theme(axis.text=element_text(size=11),
        axis.title=element_text(size=12,face="bold"))
```

Figure 2b. Predicted stock-recruitment functions for Atnarko sockeye, with observations coloured by brood cohort year, from the top-rated model (regime-shift capacity) for the 90% highest log-likelihood years.

```{r, figure 2m6, warning = FALSE}
ggplot(SR_data, aes(spawners, recruits)) +
  geom_point(aes(colour = broodyear),size=2.5) +
  scale_colour_viridis_c(name = "Year")+geom_line(data=pred_df,aes(x=x_new,y=y_pred_d6.1))+geom_line(data=pred_df,aes(x=x_new,y=y_pred_d6.2))+xlab("Spawners") + ylab("Recruits")+theme(axis.text=element_text(size=11),
        axis.title=element_text(size=12,face="bold"))
```

Figure 2c. Predicted stock-recruitment functions for Atnarko sockeye, with observations coloured by brood cohort year, from the top-rated model (regime-shift productivity) for the 80% highest log-likelihood years.

\pagebreak
```{r, figure3m7}
#pdf(here('figures','Figure 3.pdf'),width=8,height=6)
#ggplot(SR_data, aes(x=spawners,y=recruits)) +
#  geom_point(aes(colour = p.High_Cap),size=2.5) +
#  scale_colour_viridis_c()+geom_line(data=pred_df,aes(x=x_new,y=y_pred1))+geom_line(data=pred_df,aes(x=x_new,y=y_pred2))+ geom_text(data=SR_data, aes(x=spawners, y=recruits, label=broodyear),hjust=1.2, vjust=0.8,size=2.5)
#dev.off()

ggplot(SR_data, aes(x=spawners,y=recruits)) +
  geom_point(aes(colour = p.High_Cap),size=2.5) +
  scale_colour_viridis_c(name='P(High cap.)')+geom_line(data=pred_df,aes(x=x_new,y=y_pred_d7.1))+geom_line(data=pred_df,aes(x=x_new,y=y_pred_d7.2))+ geom_text(data=SR_data, aes(x=spawners, y=recruits, label=broodyear),hjust=1.2, vjust=0.8,size=2.5)+xlab("Spawners") + ylab("Recruits")+theme(axis.text=element_text(size=11),
        axis.title=element_text(size=12,face="bold"))
```

Figure 3a. Predicted stock-recruitment functions for Atnarko sockeye for each regime (high and low capacity regimes), with observations coloured by the median probability of being in the 'High Capacity' regime (Yellow indicating high probability and purple low probability, respectively).

```{r, figure3m6}
ggplot(SR_data, aes(x=spawners,y=recruits)) +
  geom_point(aes(colour = p.High_Prod),size=2.5) +
  scale_colour_viridis_c(name='P(High prod.)')+geom_line(data=pred_df,aes(x=x_new,y=y_pred_d6.1))+geom_line(data=pred_df,aes(x=x_new,y=y_pred_d7.1))+ geom_text(data=SR_data, aes(x=spawners, y=recruits, label=broodyear),hjust=1.2, vjust=0.8,size=2.5)+xlab("Spawners") + ylab("Recruits")+theme(axis.text=element_text(size=11),
        axis.title=element_text(size=12,face="bold"))
```

Figure 3b. Predicted stock-recruitment functions for Atnarko sockeye for each regime (high and low productivity regimes), with observations coloured by the median probability of being in the 'High Productivity' regime (Yellow indicating high probability and purple low probability, respectively).

```{r, figure4m7}
#pdf(here('figures','Figure 4.pdf'),width=8,height=6)
#ggplot(gamma_d, aes(by, prob)) +
#  geom_point(aes(colour = prob),size=3) +
#  scale_colour_viridis_c() + geom_ribbon(aes(ymin =l90, ymax =u90), alpha = 0.2) +xlab('Brood year')+ylab('Prob. of High Capacity Regime') + geom_hline(yintercept=0.5) 
#dev.off()
ggplot(gamma_d_m7, aes(by, prob)) +
  geom_point(aes(colour = prob),size=3) +
  scale_colour_viridis_c() + geom_ribbon(aes(ymin =l90, ymax =u90), alpha = 0.2) +xlab('Brood year')+ylab('Prob. of High Capacity Regime') + geom_hline(yintercept=0.5)+theme(axis.text=element_text(size=11),
        axis.title=element_text(size=12,face="bold"))
```


Figure 4a. Estimated probabilities of each brood year cohort being in the 'high capacity' regime state from 1972 to 2016, conversely, low probabilities indicate a high probability of being in a 'low capacity' regime state. Shaded area represents the 90% confidence intervals in the state probabilities.

```{r, figure4m6}
ggplot(gamma_d_m6, aes(by, prob)) +
  geom_point(aes(colour = prob),size=3) +
  scale_colour_viridis_c() + geom_ribbon(aes(ymin =l90, ymax =u90), alpha = 0.2) +xlab('Brood year')+ylab('Prob. of High Productivity Regime') + geom_hline(yintercept=0.5)+theme(axis.text=element_text(size=11),
        axis.title=element_text(size=12,face="bold"))

```

Figure 4b. Estimated probabilities of each brood year cohort being in the 'high productivity' regime state from 1972 to 2016, conversely, low probabilities indicate a high probability of being in a 'low productivity' regime state.
Shaded area represents the 90% confidence intervals in the state probabilities.uctivity


\pagebreak
## Reference points

$S_{max}$: Histogram of the estimated spawner escapement that maximizes recruitment. Note that esitmates are truncated here (for visual purposes) at the 90% upper estimate to remove extremely high estimates on the tails of the parameters for each regime.

```{r, S_max_m2}
#pdf(here('figures','Smax_highCap.pdf'),width=8,height=6)
#hist(d$S_max[(d$S_max[,1]<quantile(d$S_max[,1],0.9)),1],main='S_max, High Capacity Regime',xlab='spawners')
#dev.off()

#pdf(here('figures','Smax_lowCap.pdf'),width=8,height=6)
#hist(d$S_max[(d$S_max[,2]<quantile(d$S_max[,2],0.9)),2],main='S_max, Low Capacity Regime',xlab='spawners')
#dev.off()

hist(d2$S_max[(d2$S_max<quantile(d2$S_max,0.9))],main='S_max',xlab='spawners')
```

Figure 5a. Histogram  corresponds to the top-ranked model (autocorrelated Ricker) for the full predictive samples from 1987 to 2016. 
 
```{r, S_max_m7}
par(mfrow=c(1,2))
hist(d7$S_max[(d7$S_max[,1]<quantile(d7$S_max[,1],0.9)),1],main='S_max, High Capacity Regime',xlab='spawners');hist(d7$S_max[(d7$S_max[,2]<quantile(d7$S_max[,2],0.9)),2],main='S_max, Low Capacity Regime',xlab='spawners')
```

Figure 5b. This figure corresponds to the top-ranked model (regime-shift capacity) for the 90% highest predictive accuracy years - indicating the $S_{max}$ differences in each regime.

```{r, S_max_m6}
hist(d6$S_max[(d6$S_max<quantile(d6$S_max,0.9))],main='S_max',xlab='spawners')
```

This figure corresponds to the top-ranked model (regime-shift productivity) for the 80% highest predictive accuracy years.

\pagebreak
$S_{msy}$: Histogram of the estimated spawner escapement that would produce (theoretical) maximum sustainable yield (MSY). Note that esitmates are truncated here (for visual purposes) at the 90% upper estimate to remove extremely high estimates on the tails of the parameters for each regime.

```{r, S_msy_m2}
#pdf(here('figures','Smsy_highCap.pdf'),width=8,height=6)
#hist(d$S_msy[(d$S_msy[,1]<quantile(d$S_msy[,1],0.9)),1],main='S_msy, High Capacity Regime',xlab='spawners')
#dev.off()

#pdf(here('figures','Smsy_lowCap.pdf'),width=8,height=6)
#hist(d$S_msy[(d$S_msy[,2]<quantile(d$S_msy[,2],0.9)),2],main='S_msy, Low Capacity Regime',xlab='spawners')
#dev.off()

hist(d2$S_msy[(d2$S_msy<quantile(d2$S_msy,0.9))],main='S_msy, Autocorrelated Ricker',xlab='spawners')
```

Figure 6a. This figure corresponds to the top-ranked model (autocorrelated Ricker) for the full predictive samples from 1987 to 2016. 

```{r, S_msy_m7}
par(mfrow=c(1,2))
hist(d7$S_msy[(d7$S_msy[,1]<quantile(d7$S_msy[,1],0.9)),1],main='S_msy, High Capacity Regime',xlab='spawners')
hist(d7$S_msy[(d7$S_msy[,2]<quantile(d7$S_msy[,2],0.9)),2],main='S_msy, Low Capacity Regime',xlab='spawners')
```

Figure 6b. This figure corresponds to the top-ranked model (regime-shift capacity) for the 90% highest predictive accuracy years - indicating the $S_{msy}$ differences in each regime.

```{r, S_msy_m6}
par(mfrow=c(1,2))
hist(d6$S_msy[(d6$S_msy[,2]<quantile(d6$S_msy[,2],0.9)),2],main='S_msy, High Productivity Regime',xlab='spawners')

```

Figure 6c. This figure corresponds to the top-ranked model (regime-shift productivity) for the 90% highest predictive accuracy years - indicating the $S_{msy}$ differences in each regime.

\pagebreak

$U_{msy}$: The corresponding maximum sustainable annual exploitation rate is shared between both regimes, since it depends on the shared productivity parameter.

```{r, U_msy_m2}
#pdf(here('figures','U_msy.pdf'),width=8,height=6)
#hist(d$U_msy,main='U_msy',xlab='exploitation rate')
#dev.off()

hist(d2$U_msy,main='U_msy',xlab='exploitation rate',xlim=c(0,1))
```

Figure 7a. This figure corresponds to $U_{msy}$ from the top-ranked model (autocorrelated static Ricker) for the full set of predictions from 1987 to 2016.


```{r, U_msy_m7}
#pdf(here('figures','U_msy.pdf'),width=8,height=6)
#hist(d$U_msy,main='U_msy',xlab='exploitation rate')
#dev.off()

hist(d6$U_msy,main='U_msy',xlab='exploitation rate',xlim=c(0,1))
```

Figure 7b. This figure corresponds to $U_{msy}$ from the top-ranked model (regime-shift capacity) 80% highest predictive accuracy years.


```{r, U_msy_m6}
par(mfrow=c(1,2))
hist(d6$U_msy[,2],main='U_msy, High Productivity Regime',xlab='exploitation rate',xlim=c(0,1))
hist(d6$U_msy[,1],main='U_msy, Low Productivity Regime',xlab='exploitation rate',xlim=c(0,1))
```

Figure 7c. This figure corresponds to $U_{msy}$ from the top-ranked model (regime-shift productivity) for the 80% highest predictive accuracy years - indicating the $U_{msy}$ differences in each regime.

## Ecosystem-level Covariates of Productivity

In this section, we will explore some ecosystem covariates that may have an influence on productivity in Atnarko sockeye.

To begin let's visualize the annual deviations in productivity, $log(R/S)$, relative to the expectation from the static autocorrelated Ricker function for this stock:

```{r, Figure 8}
ggplot(resid.df, aes(by, resids)) +
  geom_hline(yintercept=0)+geom_line(aes(by,resids))+
  geom_point(aes(colour = by),size=3) +
  scale_colour_viridis_c(name = "Year",) + geom_ribbon(aes(ymin =resid.l90, ymax=resid.u90), alpha = 0.2) +xlab('Brood year')+ylab('Annual Productivity Deviation')+theme(axis.text=element_text(size=11),
       axis.title=element_text(size=12,face="bold"))
```

Figure 8. Annual deviations in productivity $log(R/S)$ through time.

\pagebreak
Next let's visualize some data on potential ecosystem-level drivers compiled by W. Atlas. These include:

A) Hatchery chum fry abundance - the number of chum fry released in the system lagged 2-years to reflect competition with sockeye juveniles with 1-year of freshwater rearing.

B) Pink salmon abundance - pink salmon abundance averaed over 2-3 winters where sockeye may be in competition at sea.

C) Sea surface temperature (SST) - annual SST anomalies sampled at the Pine Island lighthouse.

D) North Pacifc Gyre Oscillation (NPGO) index - NPGO during the 2nd winter of marine residency.

```{r, figure 9c,figure.width=16,figure.height=16}
colnames(SR_data2) <- make.unique(names(SR_data2))
fg9a=ggplot(SR_data2, aes(year, cm_fry_lag))+geom_line(aes(year,cm_fry_lag), alpha = 0.3)+
  geom_point(aes(colour = year),size=2.5) +xlab('Year')+ylab('Chum fry')+
  scale_colour_viridis_c(name = "Year")+theme(axis.text=element_text(size=11),
       axis.title=element_text(size=12,face="bold"))
 
fg9b=ggplot(SR_data2, aes(year, pk_avg))+geom_line(aes(year,pk_avg), alpha = 0.3)+
  geom_point(aes(colour = year),size=2.5) +xlab('Year')+ylab('Pink abundance')+
  scale_colour_viridis_c(name = "Year")+theme(axis.text=element_text(size=11),
       axis.title=element_text(size=12,face="bold"))

fg9c=ggplot(SR_data2, aes(year, SST_pine_yr))+geom_line(aes(year,SST_pine_yr), alpha = 0.3)+
  geom_point(aes(colour = year),size=2.5) +xlab('Year')+ylab('SST Anomaly')+
  scale_colour_viridis_c(name = "Year")+theme(axis.text=element_text(size=11),
       axis.title=element_text(size=12,face="bold"))

fg9d=ggplot(SR_data2, aes(year, NPGO_2wint))+geom_line(aes(year,NPGO_2wint), alpha = 0.3)+
  geom_point(aes(colour = year),size=2.5) +xlab('Year')+ylab('NPGO Index')+
  scale_colour_viridis_c(name = "Year")+theme(axis.text=element_text(size=11),
       axis.title=element_text(size=12,face="bold"))

legend = get_legend(fg9a)

tp9=plot_grid(fg9a + theme(legend.position="none"),
              fg9b + theme(legend.position="none"),
              fg9c + theme(legend.position="none"),
              fg9d + theme(legend.position="none"),
              ncol=2,nrow=2,labels=c("A","B","C","D"))

plot_grid(tp9,legend,rel_widths = c(3,.3))
```

Figure 9. Trends in each ecosystem-level variable.

\pagebreak
Let's similarly visualize the productivity residuals against these various indices:

```{r, figure 10,figure.width=16,figure.height=16}

fg10a=ggplot(SR_data2, aes(cm_fry_lag, resids))+
  geom_point(aes(colour = year),size=2.5) +xlab('Chum fry')+ylab('Prod. deviations')+scale_colour_viridis_c(name = "Year")+theme(axis.text=element_text(size=11),
       axis.title=element_text(size=12,face="bold"))
 
fg10b=ggplot(SR_data2, aes(pk_avg, resids))+
  geom_point(aes(colour = year),size=2.5,show.legend = FALSE) +xlab('Pink abundance')+ylab(NULL)+scale_colour_viridis_c(name = "Year")+theme(axis.text=element_text(size=11),
       axis.title=element_text(size=12,face="bold"))

fg10c=ggplot(SR_data2, aes(SST_pine_yr, resids))+
  geom_point(aes(colour = year),size=2.5,show.legend = FALSE) +xlab('Annual SST anomaly')+ylab('Prod. deviations')+scale_colour_viridis_c(name = "Year")+theme(axis.text=element_text(size=11),
       axis.title=element_text(size=12,face="bold"))

fg10d=ggplot(SR_data2, aes(NPGO_2wint, resids))+
  geom_point(aes(colour = year),size=2.5,show.legend = FALSE) +xlab('Winter NPGO index')+ylab(NULL)+scale_colour_viridis_c(name = "Year")+theme(axis.text=element_text(size=11),
       axis.title=element_text(size=12,face="bold"))

legend= get_legend(fg10a)

tp10=plot_grid(fg10a + theme(legend.position="none"),
              fg10b + theme(legend.position="none"),
              fg10c + theme(legend.position="none"),
              fg10d + theme(legend.position="none"),
              ncol=2,nrow=2,labels=c("A","B","C","D"))

plot_grid(tp10,legend,rel_widths = c(3,.3))

```

Figure 10. Annual deviations in productivity ($log(R/S)$) as a function of A) annual releases of chum fry, B) average abundance of pink salmon, C) annual sea surface temperature anomalies, and D) winter North Pacific Gyre Oscillation index.


The standardized linear effect size for each covariate, when included in the static autocorrelated Ricker model are as follows:

```{r, figure 11,figure.width=16,figure.height=16,warning = FALSE}
d_cov=extract(fit_2cov)

beta_cov=as.data.frame(d_cov$beta_cov)
names(beta_cov)=c('chum fry','pink abund','SST','NPGO')

f11a=ggplot(beta_cov, aes(x = beta_cov[,1])) + 
  geom_vline(xintercept=0)+
  geom_histogram(aes(y = ..density..),
                 colour = 1, fill = "darkred",bins=30) +xlim(-1.5,1.5)+xlab('Effect size')+ggtitle("Chum fry releases")+theme(axis.text=element_text(size=11),
       axis.title=element_text(size=12,face="bold"))


f11b=ggplot(beta_cov, aes(x = beta_cov[,2])) + 
  geom_vline(xintercept=0)+
  geom_histogram(aes(y = ..density..),
                 colour = 1, fill = "darkred",bins=30) +xlim(-1.5,1.5)+xlab('Effect size')+ggtitle("Pink abundance")+theme(axis.text=element_text(size=11),
       axis.title=element_text(size=12,face="bold"))


f11c=ggplot(beta_cov, aes(x = beta_cov[,3])) + 
  geom_vline(xintercept=0)+
  geom_histogram(aes(y = ..density..),
                 colour = 1, fill = "darkred",bins=30) +xlim(-1.5,1.5)+xlab('Effect size')+ggtitle("SST anomaly")+theme(axis.text=element_text(size=11),
       axis.title=element_text(size=12,face="bold"))


f11d=ggplot(beta_cov, aes(x = beta_cov[,4])) + 
  geom_vline(xintercept=0)+
  geom_histogram(aes(y = ..density..),
                 colour = 1, fill = "darkred",bins = 30) +xlim(-1.5,1.5)+xlab('Effect size')+ggtitle("NPGO")+theme(axis.text=element_text(size=11),
       axis.title=element_text(size=12,face="bold"))



plot_grid(f11a,f11b,f11c,f11d,ncol=2,nrow=2)

summary(beta_cov)
```

